Spin canonical divisors of log stacky curves

### 2015-06-23 stacky_write_up/spin_cring.tex
adding transitions to section 3

\section{Inductive Lemmata}
First we present the general inductive lemmata that will be applied
for all genera.
\todo{intro}

\ssec{General: quadratic initial ideal minimal relations}
First we prove a nice result about minimal generation of ideals of relations:

\todo{Include one of the following, if the first one, include a remark for quotient}
\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily
generated in degree 1, is equipped with a monomial ordering $\prec$.
 Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded
rings with kernel $I,$ such that $I$ is generated by elements $f_1,
\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$
is of the form $x_k$. Then, the elements $f_i$ determine minimal
generators for $I$.
\end{lem}
\begin{proof}
Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \rightarrow B
\]
\noindent
determines a map of rings, no longer necessarily graded. Consider
the grlex monomial ordering $<$ on $k[x_1, \ldots, x_n]$.
\todo{This ordering isn't quite right. 
We need to preserve the ordering on quadratic terms}
By
assumption, the kernel $I$ is generated by elements whose initial
terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

@@

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements about
generators and relations with respect to adding points.

\ssec{Inductive Theorem: Adding points for high genus}

@@

Transition to genus one.
\todo{transition!}

\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 2-Saturated Divisor}
We prove an inductive theorem on adding 2-sat here.
\todo{description}

\begin{prop}
\label{prop:sat_two_induction}
Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be tame separably rooted log stacky spin curves. 
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature 
$\sigma = (g;e_1,\ldots, e_r;\delta)$ with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
, x_5,\ldots, x_m]/I'$ and let $L = L' + \frac{1}{
3}P.$ Suppose $L$ and $L'$ satisfy $sat(Eff(L')) = sat(Eff(L)) = 2.$
Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
\end{align*}
Then, the following statements hold.
\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
		y_3$
		and equip the ring $k[y_3, y_4, x]$ with the block 
		order so that $R = k[y_3, y_4, x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x, y_3, y_4] \\
			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_4^2.\rangle
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{prop}

@@

\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 3-saturated divisor}
\label{ssec:g_0_ram_pts}

>>>>

\section{Inductive Lemmata}
First we present the general inductive lemmata that will be applied
for all genera.  We offer various inductive lemmata that will allow us to add fractional point $\frac{\alpha}{\beta}P$ to a $\mathbf{Q}$ divisor $D$ of $X$ and describe the new generators and relations of $R_{D+p}$ not in $R_D$.  Next, we provide a method specific to the case of stacky canonical divisors with no log component, which under certain conditions allows us to transfer information about the generators and relations of the half canonical ring of a stacky curve $\sx$' with signature $(g; e_1', \ldots, e_\tau'; 0)$ to a stacky curve $\sx$ with signature $(g; e_1', \ldots, e_\tau'; 0)$ where each $e_i\in \{e_i', e_i'+2\}$.

However, before we can answer these general lemmata, it is useful to prove a nice result about minimal generation of ideals of relations:
\todo{Include one of the following, if the first one, include a remark for quotient}
\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily
generated in degree 1, is equipped with a monomial ordering $\prec$.
 Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded
rings with kernel $I,$ such that $I$ is generated by elements $f_1,
\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$
is of the form $x_k$. Then, the elements $f_i$ determine minimal
generators for $I$.
\end{lem}
\begin{proof}
Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \rightarrow B
\]
\noindent
determines a map of rings, no longer necessarily graded. Consider
the grlex monomial ordering $<$ on $k[x_1, \ldots, x_n]$.
\todo{This ordering isn't quite right. 
We need to preserve the ordering on quadratic terms}
By
assumption, the kernel $I$ is generated by elements whose initial
terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

@@

With this result, we will be able to show that the sets of generators of the ideal of relations in many of the following inductive arguments are minimal.

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements under the following setup:
Let $\halfcan'$ be $\mathbf{Q}$-divisor of $X$ (and often a log half canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbf{N}$ and certain saturation conditions.  Let $\halfcan=\halfcan'+P$ for some $P$ not in the support of $\halfcan$.\todo{do we always assume this?}  Then we will explicitly describe elements that minimally generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Grobner Basis).   The proofs of these lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.

@@

\begin{lem}
\label{lem:sat_two_induction}
Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be tame separably rooted log stacky spin curves. 
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature 
$\sigma = (g;e_1,\ldots, e_r;\delta)$ with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
, x_5,\ldots, x_m]/I'$ and let $L = L' + \frac{1}{
3}P.$ Suppose $L$ and $L'$ satisfy $sat(Eff(L')) = sat(Eff(L)) = 2.$
Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
\end{align*}
Then, the following statements hold.
\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
		y_3$
		and equip the ring $k[y_3, y_4, x]$ with the block 
		order so that $R = k[y_3, y_4, x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x, y_3, y_4] \\
			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_4^2.\rangle
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{lem}

@@
